Quality Definitions of Qualities

### 2021-09-13 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Some edits to the introduction of the quality definitions paper

\usepackage{hyperref}
\hypersetup{
colorlinks=true,       % false: boxed links; true: colored links
linkcolor=red,          % color of internal links (change box color with
%linkbordercolor)
citecolor=blue,       % color of links to bibliography
filecolor=magenta,   % color of file links
urlcolor=cyan           % color of external links
}

@@

Purpose and scope of the document.  \wss{Needs to be filled in.  Should
	reference the overall research proposal, and the ``state of the practice''
	exercise in particular.}

The presentation is divided into two main sections: i) qualities that apply to
software products, software artifacts and software development processes, and
ii) qualities that are considered important for good specifications.  The
specification could be a specification of requirements, design or a test plan.

@@

\begin{description}
\item[Consistency] The final list of definitions should be consistent in the
  terminology used.  For instance, we do not use synonyms for variety; we use
  the same word to mean the same concept throughout the final list of
  definitions.  This is why measurement is given by ``the effort required..''
  and not the various synonyms for this that are seen in the literature. \wss{We
    may change this phrase we use for measuring something.  I just wanted to put
    this in here as a placeholder.}
\item[Generality]
\item[Measurability]
\item[Etc.]
\end{description}

>>>>

\usepackage{hyperref}
\hypersetup{
colorlinks=true,        % false: boxed links; true: colored links
linkcolor=red,          % color of internal links (change box color with linkbordercolor)
citecolor=blue,         % color of links to bibliography
filecolor=magenta,      % color of file links
urlcolor=cyan           % color of external links
}

@@

Purpose and scope of the document.

\wss{ Needs to be filled in.  Should reference the overall research proposal,
	and the ``state of the practice'' exercise in particular.}

Given that our research focuses on improving the quality of software, we often
find it necessary to have clear definitions of the different software qualities,
like maintainability, usability, sustainability, etc. Unfortunately, the
definitions that we find in the literature are not always satisfying.  They are
not always adequate for unambiguous communication, or they simply are	not useful
for providing guidance on what software decisions will lead to quality
improvement. Moreover, methods for measuring qualities based on the definitions
are not always clear.  Therefore, we have endeavored to build a lis of
definitions that can aid and guide our research. We are publishing our
collection, since others may likewise find them valuable.

Methodology:
\begin{itemize}
  \item Collect the list of qualities to define, based on the qualities that are
  listed in software engineering texts, such as Ghezzi Et al and VanHliet.
  \item For each quality find as many definitions as possible
  \item Based on the existing definitions, propose a high quality definition of
  each quality.  The proposed definition may use one of the existing, or combine
  several of the options.  We may also make other modifications.  The goal is
  for the proposed definition to address our acceptance criteria.
\end{itemize}

software products, software artifacts and software development processes, and
ii) qualities that are considered important for good specifications.  The
specification could be a specification of requirements, design or a test plan.

@@

\begin{description}
  \item[Unambiguous]
  \item[Consistency] The final list of definitions should be consistent in the
  terminology used.  For instance, we do not use synonyms for variety; we use
  the same word to mean the same concept throughout the final list of
  definitions.  This is why measurement is given by ``the effort required..''
  and not the various synonyms for this that are seen in the literature. \wss{We
  may change this phrase we use for measuring something.  I just wanted to put
  this in here as a placeholder.}
  \item[Generality]
  \item[Measurability]
  \item[Etc.]
\end{description}

Not necessary to have every quality measurable.  Analogy to the definition of
true error in scientific computing.

\subsection{Background}

Quality definitions history: McCall, Ghezzi et al, VanHleit, Boehm, ISO standards.
